---
Title: "CS5100 Assignment 1"
---
Task 1:

```{r}
source('GD.R')
```

Task 2:

```{r}
Auto = read.table("Auto.data" , header = T, na.strings = "?")
#attach(Auto)
High = ifelse(mpg <= 22, 0, 1)
Auto = data.frame(Auto,High)
origin = as.factor(origin)
Auto = na.omit(Auto)
Auto[,c(1:7)] = scale(Auto[,-c(8,9,10)])

```

Task 3:

```{r}
set.seed(2605)
train = sample(1:nrow(Auto), nrow(Auto)/2)
Auto.train = Auto[train,]
Auto.test = Auto[-train,]
```

Task 4:

```{r}
x_train = as.matrix(Auto.train[,c("horsepower","weight","year","origin")])
y_train = as.matrix(Auto.train[,c("High")])
W_coefficients = logistic_regression_fit(x_train,y_train,.001,10**2)
print("coefficients"); print(W_coefficients)

#Test MSE
x_test = as.matrix(Auto.test[,c("horsepower","weight","year","origin")])
y_test = as.matrix(Auto.test[,c("High")])
y_pred = logistic_regression_predict(x_test,W_coefficients)
mse_result = get_mse_result(y_pred,y_test)
print("Test MSE RESULT");print(mse_result)

#Training MSE
y_train_pred = logistic_regression_predict(x_train,W_coefficients)
mse_result_train = get_mse_result(y_train_pred,y_train)
print("Training MSE RESULT");print(mse_result_train)
```

Task 5:

```{r}
source('GD5.R')
W_coefficients_gd5 = logistic_regression_fit_gd5(x_train,y_train)
print("coefficients gd5"); print(W_coefficients_gd5)
```


Task 6:

```{r}
source('GD6.R')
repeat_gd6_plot(X_train, y_train, x_test, y_test)

```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.


